MSE and dynamic state variable model with sigma function

### 2018-05-08 doc/MSE_MAR_18.tex
continued working on description case study
Replaced table with prices by figure with price and length. The code for
this was
setwd("D://Nekane_MSE/doc/Figures")
setEPS()
postscript("prices.eps")
#png(filename=paste("MIXEDMP2_CATCH_", paste0("SIGMA ", SIGMA, ";
INCREMENTS ",control@increments, "; SIMNUMBER ",SIMNUMBER, ";
DISCARDSTEPS ",SPP1DSCSTEPS, "; MIGRATION ",migconstant, "; REC1
",paste(recs1, collapse = " "), "; REC2 ",paste(recs2, collapse = " "),
"; SP1PRICE ",paste0(round(sp1Price[,1]), sep = ', ', collapse =
''),";SP2PRICE ",paste0(round(sp2Price[,1]), sep = ', ', collapse = ''),
"

We have to implement alpha and beta, and make sure that age in VBLG is seasonal

@@

\begin{table}[!h]
\centering
\caption{Linear mass-prices estimated based on mean prices per mass age-classes. The price slopes $\beta_0$ were assumed to be similar to mean prices.}
\label{t:pricing}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{@{}lcccc@{}} 
\hline
\textbf{Market value (Euro kg\textsuperscript{-1})}& \multicolumn{4}{c}{age} \\ 
                         & 1     & 2     & 3    & 4   \\ \hline
                      \\                      
species 1 and 2            &  778  & 1354   & 1780  & 2096  \\
\\
\hline 
\end{tabular}
}
\end{table}

@@

 (six seasons) and spatially (two areas) explicit
The maximum age in the age-structured fish model was 4 years.
The two stocks are named ``stock 1" and ``stock 2". and the areas are named ``area a" and ``area b". 
In the example used for our simulations, it was assumed that there were 100 new-borns per year for both stocks. The difference between the stocks is that all new-borns of stock 1 were born in ``area a", while all new-borns of stock 2 were born in ``area b".

>>>>

We have to make sure we are clear on the ages of the species: do we start at 0 or at 1?

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=.69\textwidth]{Figures/prices.eps} 
\caption{Lenghts and prices of the species}
\end{figure}

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year. There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old
